Enhancement of SDR in Thessaloniki

### 2023-11-27 GHI_enh_01_raw_data.tex
Commit 2023-11-25 12:14
Commit 2023-11-25 14:14
Commit 2023-11-25 16:14
Commit 2023-11-27 20:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2023-11-24}

@@

\begin{verbatim}
## 
##  !! Create raw input data -> ./data/Raw_Input.Rds 
## 
##     Will read 31 input files
## 
##     Load data from Clear Sky process from original
## 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1993.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1994.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1995.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1996.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1997.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1998.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1999.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2000.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2001.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2002.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2003.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2004.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2005.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2006.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2007.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2008.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2009.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2010.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2011.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2012.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2013.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2014.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2015.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2016.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2017.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2018.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2019.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2020.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2021.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2022.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2023.Rds 
## 
##   There are  0  duplicate dates remaining!
## 
##   Extra SKIP of CM-21 data!
## 
##   Select quality data only
## 
## 
## DROP DIRECT DATA POINTS: 0 !!
## 
## 
## DROP GLOBAL DATA POINTS: 0 !!
\end{verbatim}

\begin{verbatim}
## Written:  ./figures/tbl_tsi_info.dat 
## 
## 
##   Sun Earth distance correction
## 
##   Saved raw input data: ./data/Raw_Input.Rds
\end{verbatim}

@@

\begin{verbatim}
2023-11-24 08:30:24.9 athan@sagan GHI_enh_02_process.R 6.690100 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2023-11-27}

@@

\begin{verbatim}
## 
##  !! Create raw input data -> ./data/CE_ID_Input.Rds 
## 
##     Will read 31 input files
## 
##     Load data from Clear Sky process from original
## 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1993.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1994.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1995.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1996.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1997.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1998.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1999.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2000.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2001.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2002.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2003.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2004.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2005.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2006.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2007.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2008.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2009.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2010.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2011.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2012.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2013.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2014.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2015.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2016.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2017.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2018.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2019.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2020.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2021.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2022.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2023.Rds 
## 
##   There are  0  duplicate dates remaining!
## 
##   Extra SKIP of CM-21 data!
## 
##   Select quality data only
## 
## 
## DROP DIRECT DATA POINTS: 0 !!
## 
## 
## DROP GLOBAL DATA POINTS: 0 !!
\end{verbatim}

\begin{verbatim}
## Written:  ./figures/tbl_tsi_info.dat 
## 
## 
##   Sun Earth distance correction
## 
##   Saved raw input data: ./data/CE_ID_Input.Rds
\end{verbatim}

@@

\begin{verbatim}
2023-11-27 16:57:17.7 athan@sagan GHI_enh_01_raw_data.R 5.129633 mins
\end{verbatim}
